### 2022-12-03 ms.rmd
Adding a Zoom in of the means and CIs
Trunks bigger in size

p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + 
  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") + 
  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
annotate("text", x = 1, y = 2.10, 
         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
annotate("text", x = 1.01, y = 4.60, 
         label =paste0(round(mean(change_f), 2), "%"), hjust = 0) + labs(shape = "Type") +
  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0) +

@@

  p1.2
  ggsave(p1.2, filename = "./output/figures/fig1.png")
```

>>>>

p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 4) + 
  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") + 
  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
annotate("text", x = 1, y = 2.10, 
         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
annotate("text", x = 1.01, y = 4.60, 
         label =paste0(round(mean(change_f), 2), "%"), hjust = 0) + labs(shape = "Type") +
  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0) +

@@

  p1.2
  p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
  ggsave(p1.2, filename = "./output/figures/fig1.png")
  ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
```
